Implications of taxonomic bias for microbial differential-abundance analysis

### 2022-11-18 abundance-measurement.Rmd
Normalize method of svg-to-pdf conversion
The code chunks for two svg figures differed from the others, which was
causing the pdfs to have different paths (or possibly fail to be re-generated).

```{r error-proportions, out.width = '100%', fig.cap = '(ref:cap-error-proportions)', cache = TRUE}
"figures/illustrations/error-proportions.svg" %>%
  include_svg
```

>>>>

```{r error-proportions, out.width = '100%', fig.cap = '(ref:cap-error-proportions)', cache = TRUE}
fs::path(
    "figures/illustrations/error-proportions.svg"
  ) %>%
  include_svg
```

### 2022-11-18 differential-abundance.Rmd
Normalize method of svg-to-pdf conversion
The code chunks for two svg figures differed from the others, which was
causing the pdfs to have different paths (or possibly fail to be re-generated).

```{r regression-example, fig.cap = '(ref:regression-example)', out.width = '90%'}
here::here(
  "notebook/_posts/2021-08-03-simulate-regression-example/",
  "simulate-regression-example_files/figure-html5",
  "main-figure-2-1.svg"
  ) %>%
  include_svg
```

>>>>

```{r regression-example, fig.cap = '(ref:regression-example)', out.width = '90%'}
fs::path(
  "notebook/_posts/2021-08-03-simulate-regression-example/",
  "simulate-regression-example_files/figure-html5",
  "main-figure-2-1.svg"
  ) %>%
  include_svg
```
